Concurrent Programming in Harmony

### 2021-07-22 book/paper.tex
Latest

\section*{Exercises}
\begin{problems}
\item While Harmony checks that the Validity and Agreement properties
are not violated, it does not check that the algorithm ever decides.
Indeed, in unlucky executions the algorithm may never decide.  But
how would you check that there exist execution in which the algorithm
does decide?
\item The algorithm as given works in the face of crash failures.
A more challenging class to tolerate are \emph{arbitrary failures} in
which up to \texttt{F} processors may send arbitrary messages, including
conflicting messages to different peers (equivocation).
The algorithm can tolerate those failures if you use $\mathtt{N} = 5\mathtt{F} - 1$ processors instead of $\mathtt{N} = 3\mathtt{F} - 1$.  Check that.
\end{problems}

>>>>

\section*{Exercises}
\begin{problems}
\item While Harmony checks that the Validity and Agreement properties
are not violated, it does not check that the algorithm ever decides.
Indeed, in unlucky executions the algorithm may never decide.  But
how would you check that there exist executions in which the algorithm
does decide?
\item The algorithm as given works in the face of crash failures.
A more challenging class to tolerate are \emph{arbitrary failures} in
which up to \texttt{F} processors may send arbitrary messages, including
conflicting messages to different peers (equivocation).
The algorithm can tolerate those failures if you use $\mathtt{N} = 5\mathtt{F} - 1$ processors instead of $\mathtt{N} = 3\mathtt{F} - 1$.  Check that.
\item In 1983 Michael Ben-Or presented a randomized algorithm that can
tolerate crash failures with
just $\mathtt{N} = 2\mathtt{F} - 1$ processors~\cite{BenOr83}.
Implement this algorithm.
\end{problems}
